### 2025-11-15 course/statml/2025b/project2.tex
Add files via upload

    Data download link:  \\
    \href{https://drive.google.com/drive/folders/1TrYzMUA_xLID5-gXOy_as8sH2ahLwz-l}{Google Drive Dataset}
\end{enumerate}
\bibliography{bib}

>>>>

    Data download link:  \\
    \href{https://drive.google.com/drive/folders/1TrYzMUA_xLID5-gXOy_as8sH2ahLwz-l}{Google Drive Dataset}
\end{enumerate}

\subsection{Kaggle Contest: Optiver: Trading at Stock Close}

This dataset contains historic data for the daily ten minute closing auction on the NASDAQ stock exchange. Your challenge is to predict the future price movements of stocks relative to the price future price movement of a synthetic index composed of NASDAQ-listed stocks.

This is a forecasting competition using the time series API. Data description can be found at the competition website at

\url{https://www.kaggle.com/competitions/optiver-trading-at-the-close/}

%\subsection{Data Description}
%This dataset contains historic data for the daily ten minute closing auction on the NASDAQ stock exchange. Your challenge is to predict the future price movements of stocks relative to the price future price movement of a synthetic index composed of NASDAQ-listed stocks.
%
%This is a forecasting competition using the time series API. The private leaderboard will be determined using real market data gathered after the submission period closes.
%

\bibliography{bib}
